---
editor_options:
  markdown:
    wrap: 72
---

# Homework 1

### Shannon Brown

### 09-10-2022

## Q1

#### Load quakes with data(quakes).

```{r}
data(quakes)
```

#### Show what's there with str() and summary().

```{r}
str(quakes) 
summary(quakes)
```

#### What do you see?

The class is 'data.frame' and there are 1000 rows and 5 columns. The
column names are lat, long, depth, mag, and stations. I can also see the
min, 1st quartile, median, mean, 3rd quartile, and max of each column.

## Q2

#### Show the entirety of the column long.

```{r}
quakes$long
```

## Q3

#### Hey, another useful function - unique()! Apply it to a vector,

and you can see what are all of the unique values. It's great for really
digging into a problematic vector.\
What unique stations are there?\
Use length() with unique() to determine how many stations there are.

```{r}
length(unique(quakes$stations))
```

## Q4

#### Using range(), what is the range of depths where quakes occur?

```{r}
range(quakes$depth)
```

#### Impress Yourself. Where was the earthquake of largest magnitude found? You'll need to use some comparisons and the max() function for this in your indices instead of a number!

```{r}
max(quakes$mag) 
which(quakes == 6.4, arr.ind = TRUE) 
quakes[152,]
```

lat = -15.56, long = 167.62, which is in Vanuatu

#### Meta 1. For some of you, this week was your first experience with R (or even programming at all) - how did it feel to connect concepts to a novel set of problems. For those who have experience with R, was this a cakewalk or challenging? How did it feel to shake off the cobwebs?

I took a very brief intro to R class during undergrad so some of what we
learned I knew but forgot since that was almost 2 years ago. This week
was in between a cakewalk and challenging for me. What we learned this
week wasn't super difficult to understand, it was just the amount of
material in a short period of time that's slightly overwhelming.

#### Meta 2. How much time did this take you, roughly?

Around a half hour.

#### Meta 3. Please give yourself a weak/sufficient/strong assessment on this assignment. Feel free to comment on why.

I would give myself a sufficient because I had to go back and look at my
notes to do most of this.
